Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-08-03 sections/introduction.tex
added punctuations to the second sentence for disambiguation

\section{Introduction}
Software code review is a well-established software quality management practice.
Fundamentally the intent is to identify defects early and encourage quality development policy and practices such as adherence to coding standards and improving code readability.
Traditionally code reviews were a highly structured activity. Nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} are commonly used within both industry and OSS projects. 
One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
Reviewers can find problems in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
Developers then improve the changes in response to these comments and re-submit for review until the changes are approved.  
%Fig. \ref{fig:process} illustrates a typical MCR process. 
The popularity of MCR and readily available data have made it an attractive research area.  
In particular, because performance of code review has a clear relationship to the quality of the software, many studies have investigated the factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013} effectiveness.
However, little research exists investigating \emph{how} review discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it's possible that comments can either positively contribute to the proposed changes (i.e. are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e. relatively ``\emph{useless}''). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to focus on trivial issues (e.g. coding styles), leaving deeper and possibly more quality-important issues undiscussed \cite{Bacchelli2013a}.
%This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
This is a concern because a low-degree of useful comments may degrade the overall effectiveness and perceived utility of MCR.

>>>>

\section{Introduction}
Software code review is a well-established software quality management practice.
Fundamentally, the intent is to identify defects early and encourage quality development policy and practices (such as adherence to coding standards and improving code readability).
Traditionally, code reviews were a highly structured activity, but nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} are commonly used within both industry and OSS projects. 
One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
Reviewers can find problems in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
Developers then improve the changes in response to these comments and re-submit for review until the changes are approved.  
%Fig. \ref{fig:process} illustrates a typical MCR process. 
The popularity of MCR and readily available data have made it an attractive research area.  
In particular, because performance of code review has a clear relationship to the quality of the software, many studies have investigated the factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013} effectiveness.
However, little research exists investigating \emph{how} review discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it's possible that comments can either positively contribute to the proposed changes (i.e. are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e. relatively ``\emph{useless}''). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to focus on trivial issues (e.g. coding styles), leaving deeper and possibly more quality-important issues undiscussed \cite{Bacchelli2013a}.
%This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
This is a concern because a low-degree of useful comments may degrade the overall effectiveness and perceived utility of MCR.
